---
title: "Project_Proposal"
authors: Kellie Johnson, JT Galla, and Finn Doherty
output:
  pdf_document: default
  html_document: default
---

```{r}
library(readr)
library(tidyverse)
```

```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      comment = "#>", highlight = TRUE)
```

## Non-Voters Dataset

Research Question: How do party affiliation and past experiences correlate with 
attitudes towards voting?

H0: There is no connection between party affiliation and past voting experiences
as attitude towards voting.
H1: Democrats with poor past voting experiences are the least likely to be 
devoted to voting.
H2: Neither party is more likely to be devoted to voting, but those with poor
past experiences are less likely.

This data comes from polling done by Ipsos on behalf of FiveThirtyEight. 
The survey was done online. Each observation is one respondent. These responses
were then joined with voting records by Aristotle. This resulted in 5,399 
matching responses, which are the observations in the dataset. Each variable 
represents a part of a question, outlined in nonvoters_codebook.pdf. There are
119 columns. The most relevant variables to our research question are: Q2_1 
(the importance of voting for being a good American), Q14 (if the Republican 
party wants them to vote), Q15 (if the Democratic party wants them to vote), Q16
(how easy it is to vote), Q18_1 through Q18_10 (past bad experiences with 
voting), Q21 (will they vote in 2020), Q23 (Biden or Trump), Q27_1 through Q27_6
(when have they voted), Q28_1 through Q28_8 (why they voted), Q29_1 through 
Q29_10 (why they didnt vote), Q30 (party affiliation), VOTER_CATEGORY (how often
they voted), RACE (race).

```{r non-voter}
nonvoters_data <- read_csv("nonvoters_data.csv")
glimpse(nonvoters_data)
```


## Earthquake Dataset

Research Question: How does previous earthquake experience affect relative fear
of the 'Big One' happening?

H0: There is no connection between previous earthquake experience and fear of
the 'Big One' happening.
H1: Experiencing any earthquake at some point in your past results in a greater
likelihood that you fear the 'Big One' happening.
H2: Experiencing a major earthquake at some point in your past results in a 
greater likelihood that you fear the 'Big One' happening.

This data comes from a poll by SurveyMonkey Audience that FiveThirtyEight 
commissioned. The data consists of 1013 observations, each one matching one 
response, made up of people across America. The responsers had varying genders,
locations, income level, and ages. The dataset also consists of 11 variables,
some demographic like the varying parameters aforementioned, and others specific
to earthquake data, such as previous experience and fear of 'The Big One' 
happening. The most relevant variables to this study will be the "How worried 
are you about the 'Big One,' a massive, catastrophic earthquake?" and the
"Have you ever experienced an earthquake?" questions. For clarification, the 
'Big One' is a term to describe the San Andreas Fault having a supermassive
earthquake, one that has been sensationalized in various movies. 

```{r non-voter}
earthquake_data <- read_csv("earthquake_data.csv")
glimpse(earthquake_data)
```
